---
title: "Creating this package's sticker"
---

```{r}
#| include: false
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

Quick article to document the process of creating a sticker for this package (which I initially did for fun and learning purposes). I use the `pacman` package in my setup to conveniently check "if installed"/install/load the necessary packages, all in one go.

```{r}
#| label: setup
#| eval: true

if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}

pacman::p_load(
  # cropcircles, # to crop the image in a hexagonal shape
  ggplot2, 
  ggpath,   # to read the images directly from the paths
  here,     # to use relative paths
  knitr,    # to include the images in the article
  showtext, # to use a custom font
  sysfonts # to use a custom font
  )
# cropcircles is commented because it has a weird interference with GHA
```

It all starts with a little square shaped drawing of mine, named `delemr_drawing.png`. 

```{r out.width="50%", alt="Raw image of my drawing."}
#| label: draw
#| fig.alt: >
#|   Raw image of my drawing.

image_path <- "delemr_drawing.png"
stick_path <- "delemr_sticker.png" # our eventual sticker

knitr::include_graphics(image_path)
```


Time to build the sticker. 

- I used the `hex_crop()` function to crop the image in a hexagonal shape, 
with a border of a specified color and size. 
I had to dug a bit to find the exact grey-blue colour of the GitHub website lines to use as the border colour for a cool "merging with the background" effect.
- I used a custom font to write the package name on the sticker, 
namely "*Poiret One*" font from Google Fonts. 
I loaded it with `sysfonts::font_add_google()` and `showtext::showtext_auto()`.
- I used `ggplot2` to plot the cropped image and the package name on top of it, 
angled and styled using `ggplot2::annotate()`. 
I used `ggplot2::theme_void()` to remove everything besides the image.
- I saved the sticker with `ggplot2::ggsave()` and the appropriate dimensions.

```{r}
#| label: sticker
#| fig-width: 5.18
#| fig-height: 6
#| fig.alt: >
#|   Final sticker with the package name.
#| eval: false

raw_cropped <- hex_crop(
  images = image_path,
  border_colour = "#394049",
  border_size = 7
)

font <- "Poiret One" 
font_add_google(font)
showtext_auto()

# building the sticker
p <- 
  ggplot() + 
  geom_from_path(aes(.5, .5, path = raw_cropped)) +
  annotate(
    "text",
    x = .24,
    y = .22,
    label = "delemr",
    color = "white",
    family = font,
    size = 54,
    angle = -30
  ) +
  scale_x_continuous(limits = c(0, 1), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0, 1), expand = c(0, 0)) +
  theme_void()

# saving it
ggsave(
  filename = stick_path, plot = p,
  width = 5.18, height = 6,
  dpi = 300
  )
```

```{r out.width="50%", alt="Final sticker with the package name."}
knitr::include_graphics(stick_path)
```

Now to use the sticker as a package logo, it needs to be a bit smaller, 
and this is conveniently taken care of by the `usethis::use_logo()` function.

```{r}
#| label: logo
#| eval: false

usethis::use_logo(stick_path)
```

Done!
